Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-11-19 manuscript/manuscript.tex
comments on some figures; added chance article to bib

@@

@@

\begin{table}[tbp]
  \centering
  \caption{Sample  Negative Durations [excluding extreme values that are <$-$730 days]}
   \label{tab:largest-errors}
 	\begin{tabular}{l l l r l}
    \toprule
    \texttt{created\_date} & \texttt{closed\_date} & Duration (days)}  & {Agency} \\
    \midrule
    2023-01-27 14:40:00 & 2022-01-14 14:40:00 & $-$378 & DOT \\
    2023-01-18 10:06:00 & 2022-01-12 10:06:00 & $-$371 & DOT \\
    2023-01-27 14:36:00 & 2022-01-22 14:35:00 & $-$370 & DOT \\
    2023-01-11 11:10:00 & 2022-01-09 11:10:00 & $-$367 & DOT \\
    2023-12-18 03:13:00 & 2023-01-16 13:10:00 & $-$335 & DOT \\
    \bottomrule
    \end{tabular}
 \end{table}

@@

\subsection{Accuracy and Precision:}
\label{sec:precision}
An question of precision vs. accuracy arises with the \texttt{latitude} 
and \texttt{longitude} fields. as well as with the duplicative 
\texttt{location} field. These fields are expressed as
\jy{This is a artifact of R reading them in as doubles. Single
  precision should be sufficient as illustrated in my Chance manuscript.}
a 14\mbox{-}decimal number, e.g. \texttt{latitude} 40.86769186022511. 
Given that 1 degree of latitude at the equator is equal to 111.04 
kilometers, the ``1'' at the end of the decimal number represents 
approximately 1.1 nanometers (1/1,000,000,000 of a meter). (For 
reference a DNA molecule is approximately 2 nanometers in width.) The 
representation of the \texttt{latitude} and \texttt{longitude} fields
appears to be a classic case of extreme precision, but limited 
accuracy. All the \texttt{latitude}, \texttt{longitude}, and \texttt{location}
fields display this characteristic.

@@

\subsection{Data Dictionary} 
\label{sec:datadictionary}
The \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary} would greatly benefit from an update. We found several discrepancies between the 
Data Dictionary and the actual data, which could potentially 
mislead analytic efforts. Here are some examples:

@@

\section*{Supplementary Material}
The NYC 311 SR data and code used to produce the results reported in
this paper are available [FixMe].

>>>>

\jy{Need to avoid url links in the text. Could cite some as references
  if needed.}

\jy{No need for \mbox{-} in text.  one - is a hyphen; two -- is
  en-dash;   three --- is an em-dash.}

@@

\jy{Figures 4-6 seems taking more spaces than necessary. Fig 4 and 6
  could be on one with ggplot facet. Figure 5 too. Both using two
  panels on one row.}

@@

\begin{table}[tbp]
  \centering
  \caption{Sample  Negative Durations [excluding extreme values that are <$-$730 days]}
   \label{tab:largest-errors}
 	\begin{tabular}{l l l r l}
    \toprule
    \texttt{created\_date} & \texttt{closed\_date} & {Duration (days)}  & {Agency} \\
    \midrule
    2023-01-27 14:40:00 & 2022-01-14 14:40:00 & $-$378 & DOT \\
    2023-01-18 10:06:00 & 2022-01-12 10:06:00 & $-$371 & DOT \\
    2023-01-27 14:36:00 & 2022-01-22 14:35:00 & $-$370 & DOT \\
    2023-01-11 11:10:00 & 2022-01-09 11:10:00 & $-$367 & DOT \\
    2023-12-18 03:13:00 & 2023-01-16 13:10:00 & $-$335 & DOT \\
    \bottomrule
    \end{tabular}
 \end{table}

@@

\subsection{Accuracy and Precision:}
\label{sec:precision}
An question of precision vs. accuracy arises with the \texttt{latitude} 
and \texttt{longitude} fields. as well as with the duplicative 
\texttt{location} field. These fields are expressed as
\jy{This is a artifact of R reading them in as doubles. Single
  precision should be sufficient as illustrated in \citet{bates2024csv}.}
a 14\mbox{-}decimal number, e.g. \texttt{latitude} 40.86769186022511. 
Given that 1 degree of latitude at the equator is equal to 111.04 
kilometers, the ``1'' at the end of the decimal number represents 
approximately 1.1 nanometers (1/1,000,000,000 of a meter). (For 
reference a DNA molecule is approximately 2 nanometers in width.) The 
representation of the \texttt{latitude} and \texttt{longitude} fields
appears to be a classic case of extreme precision, but limited 
accuracy. All the \texttt{latitude}, \texttt{longitude}, and \texttt{location}
fields display this characteristic.

@@

\jy{Could refer to cross-plotform data format such as Arrow
  \citep{bates2024csv}.}

\subsection{Data Dictionary} 
\label{sec:datadictionary}

The \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary} would greatly benefit from an update. We found several discrepancies between the 
Data Dictionary and the actual data, which could potentially 
mislead analytic efforts. Here are some examples:

@@

\section*{Supplementary Material}
The NYC 311 SR data and code used to produce the results reported in
this paper are available at \url{https://github.com/jun-yan/nyc311clean}.
